\documentclass{yijiem}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}
\begin{document}

\begin{spacing}{1.2}
\name{Yijie Ma}
\end{spacing}
\contact{37242 Rico Common \#1040, Fremont, CA 94536}{yijiem.main@gmail.com}{\href{https://github.com/yijiem}{github}}{408-639-9819}

\section{Skills}
    C/C++, Python, Rust, Operating System, Networking, Distributed System, Storage System, Cross-platform\newline(Linux/macOS/Windows) software development

\section{Work Experience}
\datedsubsection{Google}{April 2017 - Present}
    \textit{\small Software Engineer}
    \projectitemsthree{gRPC Open Source Remote Procedure Call Framework}{\workitemsfour{Designed and built the cross-platform asynchronous \href{https://github.com/grpc/grpc/blob/master/src/core/lib/event_engine/ares_resolver.h}{DNS resolver}.}{Designed and built the \href{https://github.com/grpc/grpc/blob/master/src/core/telemetry/metrics.h}{Metrics framework} with C++ template technique and the \href{https://github.com/grpc/grpc/blob/master/src/cpp/ext/otel/otel_plugin.h}{OpenTelemetry plugin}.}{Co-authoered the A79: Non-per-call Metrics Architecture \href{https://github.com/grpc/proposal/blob/master/A79-non-per-call-metrics-architecture.md}{gRFC}.}{Fixed numerous crashes, security issues and made performance improvements for millions of Open Source users.}}{Google Drive Desktop application}{\workitemsfour{Built rsync-style differential compression and Gzip compression stack for content upload.}{Built USB device backup stack which backs up millions of users' files daily.}{Built Cross-platform Preference system for users and admins to configure the application.}{Made 100+ crash fixes, customer issue fixes and performance improvements.}}{Stadia Cloud Gaming Service}{\workitemsthree{Built a Cgroup library for setting up Cgroup configurations during container setup on VMs.}{Increased click-to-play speed by 75\% by optimizing the container setup.}{Built a custom shell to replace explorer.exe for gamer surface lockdown on Windows.}}
\datedsubsection{NetApp}{August 2015 - March 2017}
    \textit{\small Member of Technical Staff}
    \begin{spacing}{1.2}
    Worked on the \href{https://www.netapp.com/media/19930-ds-3651.pdf}{AltaVault} Cloud-Integrated Storage device. Built a filesystem software and used RocksDB for cataloging
    \end{spacing}
    users' snapshot data. Built full or incremental backup and restore functionalities.

\section{Education}
\datedsubsection{Carnegie Mellon University}{Sep 2013 - May 2015}
    \begin{spacing}{0.7}
    \textit{\small Master of Science in Electrical and Computer Engineering}\newline
    \end{spacing}
    \textbf{Coursework:} Introduction to Computer System, Embedded Realtime System, Advanced Storage System, Internet Service, Cloud Computing, Distributed System
\datedsubsection{Donghua University}{Sep 2009 - May 2013}
    \begin{spacing}{0.7}
    \textit{\small Bachelor of Engineering in Electrical Engineering and Automation}\newline
    \end{spacing}
    \textbf{Awards:} 2012 IEEE-standard Micromouse competition national award issued by China Computer Federation (CCF)
\end{document}
